What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Work on the parse + plot examples

\subsection{Minimized expressions}

@@

\mypara{Capturing a call.}  A common use case for \eval is to be combined with \c{match.call}.
\c{match.call} walks up the call stack, captures the code that invoked the
currently executing function, and returns it as an unevaluated expression that includes the call function and its unevaluated arguments. The
pattern is to transform a call to some function \c{f} into a call to \c{g} with
some arguments retained and others modified.  \todo{or change the target
function. Both are described as "patterns" in the R documentation.} As an
illustration, consider the \c{vcpart} package's function \c{tvcglm} that is
translated to a call to \c{tvcm} with two modifications to the argument list:
argument \c{control} can't be missing and \c{fit} is set \c{"glm"}. The
function ends with a call to \c{eval.parent} to ensure that the rewritten call
is evaluated in the same environment the original call was.  \begin{lstlisting}
tvcglm <- function(formula, data, family, ...) { k <- match.call() k[[1]] <-
as.name("tvcm") if ("fit" %in% names(list(...))) warning("'fit' ignored.")
k$fit <- "glm" eval.parent(k) } \end{lstlisting} This pattern is recognizable
by the fact that the expression is a call and the target environment is that of
the parent. \todo{Remove that example}

@@

In package \emph{survival}\footnote{It is a \emph{recommended package}, so recommended by the CRAN maintainers, thoroughly tested, and following R best practices.}, in function \c{coxph}, the surrounding call is first captured, then \c{model.frame} is injected as the function name in the call, and finally, the new call is evaluated in the parent frame.

@@

@@

\mypara{Code Generation.} The more traditional use of \eval is to execute code
that was assembled by the programmer into a string. Here we show the method
\c{plot} for class \c{sback} in package \c{wsbackfit}, simplified for
explanatory purposes. The function takes a long argument list, the names of
which are captured in the list \c{opt}. The string \c{stub} is composed of a
subset of the arguments passed to this function; the variable is used to
construct a call to \c{base::plot} which will draw a plot. \NOTE{This example
  is a bit messed up. What is var? Does the use of ... in the eval grab the
arguments of this call? If yes does it not end up with xlab twice? HELP}
\todo{Does this comment still applies?} The \parse and \eval combination is
used by the the \source function in the base library to load R code from a file
in the current workspace.  \begin{lstlisting} plot.sback <- function(x,...) {
opt <- names(list(...)) stub <- paste( ifelse("xlab" %in%
opt,"",paste(",xlab=\"",var,"\"",sep="")), ifelse("type" %in%
  opt,"",",type=\"l\""), sep="") plot <-
  paste("plot(x.data,",stub,",...)",sep="") eval(parse(text=plot))
  \end{lstlisting} This pattern is recognizable by its use of \c{parse} to turn
  a string into an expression.

  \todo{Put a simpler example, again with building a plot}

@@

>>>>

\subsection{Shapes of \eval}

@@

\mypara{Capturing a call.}  A common use case for \eval is to be combined with \c{match.call}.
\c{match.call} walks up the call stack, captures the code that invoked the
currently executing function, and returns it as an unevaluated expression that includes the call function and its unevaluated arguments. The
pattern is to transform a call to some function \c{f} into a call to \c{g} with
some arguments retained and others modified. This pattern is recognizable
by the fact that the expression is a call and the target environment is that of
the parent.

@@

In package \emph{survival}\footnote{It is a \emph{recommended package}, so recommended by the CRAN maintainers, thoroughly tested, and following R best practices.}, in function \c{coxph}, the surrounding call is first captured, then \c{model.frame} is injected as the function name in the call, and finally, the new call is evaluated in the parent frame, to ensure that the rewritten call
is evaluated in the same environment the original call was.

@@

\c{substitute} can be used to capture only a part of the call, \ie one of the arguments.

@@

\mypara{Code Generation.} The more traditional use of \eval is to execute code
that was assembled by the programmer into a string. Here we show the method
\c{plot} for class \c{gmap} in package \c{gpmaps}, simplified for
explanatory purposes.   \c{paste} is used to dispatch to a specialized plot function, among \c{plot2\_orig},  \c{plot3\_orig}, \c{plot3\_dec} and so on.
\begin{lstlisting}
eval(parse(text=paste('plot',gpmap$nloci,'_orig(gpmap)',sep="")))
\end{lstlisting}

 \todo{Add an example of a plot with parse from Kaggle}

The \parse and \eval combination is
used by the \source function in the base library to load R code from a file
in the current workspace.

@@

\todo{There is an example in package comprenhr that does code generation with substitute to create list comprehensions, but it is quite difficult to grasp.}
